QPLIB: A Library of Quadratic Programming Instances

### 2017-01-30 QPLIB-1.0.tex
fix some latex warnings

\begin{center}
\begin{longtable}{ lcl }

@@

\multicolumn{3}{l}{\multirow{1}{\textwidth}{$^{\ddagger}$Applications with many manuscripts cite reviews and recent works \\[-12pt] \phantom{hi} \hfill \emph{continued}}} \\ \\

@@

\multicolumn{3}{l}{\multirow{1}{\textwidth}{$^{\ddagger}$Applications with many manuscripts cite reviews and recent works.}} \\ \\ \\

@@

\multirow{1}{.55\textwidth}{Quadratic Assignment Problem (QAP)$^{\ddagger}$} & \checkmark & \cite{anstreicher:2003,loiola-etal:2007} \\ \cmidrule(rl){2-3}

@@

\multirow{1}{.55\textwidth}{Layout design} & \checkmark & \cite{anjos-liers:2012,castillo-etal:2005,dorneich-sahinidis:1995} \\ \cmidrule(rl){2-3}

@@

\multirow{1}{.55\textwidth}{Maximizing polygon dimensions} && \cite{audet-etal:2011,audet-etal:2007,Audet-etal:2009,audet-etal:2002,Audet-Ninin:2013} \\ \cmidrule(rl){2-3}

@@

\textbf{Finance} \\
Portfolio optimization & \checkmark & \multirow{1}{.25\textwidth}{\cite{deng-etal:2013,kallrath:2003,lin-etal:2005,maranas-etal:1997,parpas-rustem:2006,rios-sahinidis:2010,FrFG16,FrGe06a,FrGe07a,FrGe09a}} \\ \\

@@

\multirow{1}{.55\textwidth}{Crude oil scheduling} & \checkmark & \cite{li-etal:2007,li-etal:2011,li-etal:2012,mouret-etal:2009,mouret-etal:2011} \\ \cmidrule(rl){2-3}

@@

\multirow{1}{.55\textwidth}{Data reconciliation} & \checkmark & \cite{ruiz-grossmann:2011} \\ \cmidrule(rl){2-3}

@@

\multirow{1}{.55\textwidth}{Multi-commodity flow} & \checkmark & \cite{tadayon-smith:2013} \\ \cmidrule(rl){2-3}

@@

\multirow{1}{.55\textwidth}{Quadratic network design} & \checkmark & \cite{FrFG16,FGGP11} \\ \cmidrule(rl){2-3}

@@

\multirow{1}{.55\textwidth}{Multi-period blending} & \checkmark & \cite{kolodziej-etal:2013:jogo,kolodziej-etal:2013} \\ \cmidrule(rl){2-3}

@@

\multirow{1}{.55\textwidth}{Natural gas networks} & \checkmark & \cite{hasan-etal:2011,li-etal:2011-aiche_journal,li-etal:2011-jogo} \\ \cmidrule(rl){2-3}

@@

Pooling$^{\ddagger}$ & \checkmark & \multirow{1}{.25\textwidth}{\cite{Alfaki-Haugland:2013,Castillo-etal:2013,dambrosio-etal:2011pooling,Faria-Bagajewicz:2012,misener-floudas:2009,misener-floudas:2010-genpooling,Papageorgiou-etal:2012,pham-etal:2009,ruiz-etal:2013}} \\ \\ \cmidrule(rl){2-3}

@@

\multirow{1}{.55\textwidth}{Open-pit mine scheduling} & \checkmark & \cite{bley-etal:2012} \\ \cmidrule(rl){2-3}

@@

Water networks$^{\ddagger}$ & \checkmark & \multirow{1}{.25\textwidth}{\cite{ahmetovic-grossmann:2010,bagajewicz:2000,bragalli-etal:2011,castro-teles:2013,geissler-etal:2013,gleixner-etal:2012,jezowski-2010,khor-etal:2014,ponceortega-etal:2010,teles-etal:2012}} \\ \\

@@

\multirow{1}{.55\textwidth}{Traveling Salesman Problem with Neighborhoods} & \checkmark & \cite{gentilini-etal:2013} \\ \\

@@

\multirow{1}{.55\textwidth}{Delay-constrained routing} & \checkmark & \cite{FrGaSc14,FrGaSt16a} \\

@@

\multirow{1}{.55\textwidth}{Unit-commitment} & \checkmark & \cite{FrFG16,FrGe06a,FrGe09a,Tetal15} \\

@@

\multirow{1}{.55\textwidth}{Controlled Tabular Adjustment} & \checkmark & \cite{CaFG14} \\

@@

\end{center}

>>>>

\begin{longtable}[c]{lcl}

@@

\multicolumn{3}{l}{\multirow{1}{.95\textwidth}{$^{\ddagger}$Applications with many manuscripts cite reviews and recent works \\[-12pt] \phantom{hi}  \hfill\emph{continued}}}

@@

\multicolumn{3}{l}{\multirow{1}{.95\textwidth}{$^{\ddagger}$Applications with many manuscripts cite reviews and recent works.}}

@@

Quadratic Assignment Problem$^{\ddagger}$ & \checkmark & \cite{anstreicher:2003,loiola-etal:2007} \\ \cmidrule(rl){2-3}

@@

Layout design & \checkmark & \cite{anjos-liers:2012,castillo-etal:2005,dorneich-sahinidis:1995} \\ \cmidrule(rl){2-3}

@@

Maximizing polygon dimensions && \cite{audet-etal:2011,audet-etal:2007,Audet-etal:2009,audet-etal:2002,Audet-Ninin:2013} \\ \cmidrule(rl){2-3}

@@

\multicolumn{3}{l}{\textbf{Finance}} \\[1pt]
Portfolio optimization & \checkmark & \multirow{1}{.3\textwidth}{\cite{deng-etal:2013,kallrath:2003,lin-etal:2005,maranas-etal:1997,parpas-rustem:2006,rios-sahinidis:2010,FrFG16,FrGe06a,FrGe07a,FrGe09a}} \\ \\

@@

Crude oil scheduling & \checkmark & \cite{li-etal:2007,li-etal:2011,li-etal:2012,mouret-etal:2009,mouret-etal:2011} \\ \cmidrule(rl){2-3}

@@

Data reconciliation & \checkmark & \cite{ruiz-grossmann:2011} \\ \cmidrule(rl){2-3}

@@

Multi-commodity flow & \checkmark & \cite{tadayon-smith:2013} \\ \cmidrule(rl){2-3}

@@

Quadratic network design & \checkmark & \cite{FrFG16,FGGP11} \\ \cmidrule(rl){2-3}

@@

Multi-period blending & \checkmark & \cite{kolodziej-etal:2013:jogo,kolodziej-etal:2013} \\ \cmidrule(rl){2-3}

@@

Natural gas networks & \checkmark & \cite{hasan-etal:2011,li-etal:2011-aiche_journal,li-etal:2011-jogo} \\ \cmidrule(rl){2-3}

@@

Pooling$^{\ddagger}$ & \checkmark & \multirow{1}{.3\textwidth}{\cite{Alfaki-Haugland:2013,Castillo-etal:2013,dambrosio-etal:2011pooling,Faria-Bagajewicz:2012,misener-floudas:2009,misener-floudas:2010-genpooling,Papageorgiou-etal:2012,pham-etal:2009,ruiz-etal:2013}} \\ \\ \cmidrule(rl){2-3}

@@

Open-pit mine scheduling & \checkmark & \cite{bley-etal:2012} \\ \cmidrule(rl){2-3}

@@

Water networks$^{\ddagger}$ & \checkmark & \multirow{1}{.3\textwidth}{\cite{ahmetovic-grossmann:2010,bagajewicz:2000,bragalli-etal:2011,castro-teles:2013,geissler-etal:2013,gleixner-etal:2012,jezowski-2010,khor-etal:2014,ponceortega-etal:2010,teles-etal:2012}} \\ \\

@@

Traveling Salesman Problem \\
with Neighborhoods & \checkmark & \cite{gentilini-etal:2013} \\

@@

Delay-constrained routing & \checkmark & \cite{FrGaSc14,FrGaSt16a} \\

@@

Unit-commitment & \checkmark & \cite{FrFG16,FrGe06a,FrGe09a,Tetal15} \\

@@

Controlled Tabular Adjustment & \checkmark & \cite{CaFG14}

@@
